prolfqua - R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-03-18 inst/MyArticle/paper.Rmd
Collect Abbreviations of Introduction

### P-value moderation

@@

@@

The authors thank the technology platform fund of the University of Zurich.

# References

>>>>

### $p$-value moderation

@@

The authors thank the technology platform fund (TPF) of the University of Zurich.

# Abbreviations

|       |                                                   |
|:------|:--------------------------------------------------|
|ESI-MS |Electro-Spray-Ionization Mass Spectrometry         |
|FDR    |False Discovery Rate                               |
|HPLC   |High-Pressure Liquid Chromatography                |
|LC-MS  |Liquid Chromatography followed by Mass Spectrometry|
|LFQ    |Label-Free Quantification                          |
|OO     |Object-Oriented                                    |
|MS     |mass spectrometry                                  |

# References {-}

<div id="refs"></div>

@@

## Session information

```{r sessioninfo, echo=FALSE}
sessionInfo()
```
